---
title: "SOST71032 Social Network Analysis Assessment II"

date: "4/25/2021"
output:
  pdf_document: default
  html_document: default
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("rmarkdown")
library("knitr")
```

##### Assessment II Part A: Lazega’s Lawyers

## Problem a) 

##### Loading dataset and libraries 

```{r dataset}
LazNet <- read.table('/Users/xiaoni/Downloads/lazcowork.txt')
colnames(LazNet)<-c(1:36)
LazAtt <- read.table('/Users/xiaoni/Downloads/lazpractice.txt')
library(RSiena)
library('igraph')
```

##### Visulisation

```{r visulisation1}
m <- as.matrix(LazNet)
mode(m) <- "numeric"

net <- graph.adjacency(m, mode = "undirected", weighted = TRUE, diag = FALSE)
plot(net)
```

##### Number of nodes

```{r nodes}
node<- gorder(net)
node
```


##### Number of edges

```{r edges}
edge <- gsize(net)
edge
```

##### Density

```{r density}
# density captures how many edges there are in a network divided 
# by the total possible number of edges
edge/(((node)*(node-1))/2)
```

##### Conclustion

```{r conclustion1}
# Number of nodes is 36, number of edges is 115 and density is 0.1825397.   # The low density in terms of the interactions among the members.
```

## Problem b)

##### State the hypotheses:
##### H0: There is no significant influence between practice and lawyer
##### H1: There is significant influence between practice and lawyer

##### First, get the edge list
```{r edgelist}
g <- graph.adjacency(m)
el<- get.edgelist(g)
el <- as.matrix(el)
```

##### Read attribute to dataframe
```{r readattribute}
attributes <- as.data.frame(LazAtt, stringsAsFactors = F)
```

##### Add the column names
```{r addcolumnnames}
colnames(attributes) = c("practice")
```

##### Add an ID column
```{r addid}
attributes$ID <- 1:nrow(attributes)
```

##### Indexing data so that you only put in certain columns
```{r indexing}
el_no_weight <- el[,1:2] # We will ignore the ranking variable for now.
```

##### Graph the network
```{r networkgraph}
net37 <- graph.edgelist(el_no_weight, directed = F)
net37
plot(net)
```

##### Finally, add attributes  
##### First link vertex names to their place in the attribute dataset
```{r linkvertex}
linked_ids <- match(V(net37)$name, attributes$ID)
linked_ids
```

##### Then we can use that to assign a variable to each user in the network
```{r assigntonetwork}
V(net37)$practice <- attributes$practice[linked_ids]
net37
```

##### Calculate homophily
```{r homophily}
df <- data.frame(get.edgelist(net37), stringsAsFactors = F)
df$practice1 <- as.numeric(attributes$practice[match(df$X1, attributes$ID)])
df$practice2 <- as.numeric(attributes$practice[match(df$X2, attributes$ID)])
cor.test(df$practice1, df$practice2)
```

##### Conclusion

```{r con}
# H0: There is no significant influence between practice and lawyer
# H1: There is significant influence between practice and lawyer
# While here you can see the result, t score = 7.7499 which is high and p-value = 0.0002244 which is less than 0.05. 
#Therefore we will reject the null hypothesis and accept alternative hypothesis.
```

## Problem c) 
##### First Let us set up a ERGM model
##### Get libraries
```{r include=FALSE}
# install.packages("statnet")
library(statnet)
# install.packages("intergraph")
library(intergraph)
```

##### Convert it to a statnet object.
```{r statnet}
statnet37 <- asNetwork(net37)
statnet37
```

##### Plot
```{r plot}
# install.packages("statnet")
plot(statnet37, 
     vertex.col = "tomato", 
     vertex.cex = 1)
```

##### Describe what these statistics represent and why they might be of interest to include in an ERGM. 
```{r explain}
# nodecov("practice")
# Explanation: nodecov() is used for main effect of a covariate. 
# This term adds a single network statistic to the model equaling 
# the sum of attribute practice for all edges in the network. 
# This term adds a single network statistic for each quantitative 
# attribute or matrix column to the model equaling the sum of attr(i) 
# and attr(j) for all edges in the network.

# match("practice")
# Explanation: nodematch is the homophily term in ergm. 
# We can specify the attribute of "practice", which we want to 
# examine as well as the different arguments, 
# which allows for differential levels of homophily for different groups.

# gwesp(decay = 0.693)
# Explanation: In addition to the number of edges in the null model, 
# the ERGM can also control other network structure factors, 
# such as the number of binary groups in the network 
# (set in ergm by mutual interaction) and triadic closure. 
# (set in ergm via gwesp). 
# The gwesp term behaves better comparing with triangles.

```

##### Fit the mentioned ERGM and interpret the parameter estimates. 
##### Build a ERGM model 1
```{r ergm}
model1 <- ergm(statnet37 ~ edges + 
                 nodematch("practice"))
summary(model1)
```

##### Interpret
```{r interpret2}
# variable "practice" shows highly significant! 
# As the p-value is pretty small.
```

##### Build a ERGM model 2
```{r ergmmodel2}
table(V(net37)$practice) # 0 = litigation, 1 = corporate
model2 <- ergm(statnet37 ~ edges + 
                 nodematch("practice", diff = T, levels = c("0", "1")))
summary(model2)
```

##### Interpret
```{r interpret3}
# practice.1 which stands for corporate, is significant.
```

##### Build a ERGM model 3
```{r ergmmodel3}
model3 <- ergm(statnet37 ~ edges + 
                 nodematch("practice") + 
                 gwesp(0.693, fixed = T),
               control=control.ergm(MCMLE.maxit= 40))
summary(model3)
```

##### Interpret
```{r inter4}
# gwesp(decay = 0.693) is more significant than attribute practice.
```

##### Briefly explain how you would assess the goodness of fit of this model.
##### The goodness-of-fit statistics for this most elaborate model
```{r goodnessoffit}
model3_gof <- gof(model3, control.gof.formula(nsim = 100))
```

##### Visulisation
```{r visu}
par(mar = rep(2, 4))
plot(model3_gof, main = '')
```

##### Interpret
```{r inter5}
# From the visuliation, you can see an improvement over the random graph.
```


##### Part B: SAOM

##### Problem a)

##### Interpret the results. Assess the convergence of the model and discuss each effect in the table.
```{r intr1}
# Interpret: 

# The convergence t ratios all is less than 0.03, the overall maximum convergence #ratio is 0.1, 
# the algorithm is converged.

# 0. Rate presents each actor is given 8.96 micro steps 
# in which to make a change to #its network, such as add/drop 
# a tie or make no change.

# 1. The outdegree(density) is negative and highly significant, 
# which means that ties are unlikely. There are some penalty to 
# add a tie.
# That also means workplace has less co-workers more trusts.

# 2. The feature on reciprocity is positive and highly significant, which means if I 
# trust others in the workplace, the others will also trust me as well.

# 3. The transitive triplets is positive and significant, which means if I trust 
# co-worker A and co-worker B, then most likely, A and B also trust each other.

# 4. The indegree - popularity is negative, which means actors with more incoming ties 
# have a smaller likelihood receiving future ties.

# 5. The sex alter is positive (0.06), smaller than standard error (0.31), so this is 
#insiginificant. It means gender is mindness. 

# 6. The sex ego is positive but not siginificant, means sex will influence trust but 
#not so siginificantly influence.

# 7. The same sex is positive and shows significance, means co-workers with same 
# gender, trust more with each other. In another word, men trust men more, women trust 
# women more. 
```


##### Problem b)

```{r intr5}
# Simulation Explanation:

# 1. out-degree effect, controlling the density / average degree; 

# 2. reciprocity effect, number of reciprocated ties

# 3. transitive triplets effect, number of transitive patterns in its ties

# 4. same sex: +1.0, observations who have the same gender 

# Assortativity effects:Preferences of actors dependent on their

# degrees.Depending on # their own out- and in-degrees,
# actors can have differential preferences for tiesto 

# others with also high or low out- and in-degrees.

# There are 4 possibilitiese: 
# out ego - out alter degrees
# out ego - in alter degrees
# in ego - out alter degrees
# in ego - in alter degrees

# There are four observations (tA, tB, tC, tD), the relation is defined as a "trust 
# relation".
# – outdegree: -2.5;
# – reciprocity: +1.5;
# – transitive triplets: +0.5; 
# – same sex: +1.0;
# – all other parameters: 0.

# The evaluation function is fi(x) = -2.32{current outdegree} + 1.39{current 
# reciprocity} + 0.16{current transitive triplets} + 0.91 {current same sex}
# Add tie from A to D, while A is male and D is female ans same sex is positive. 
# Therefore we may do the calculations with same sax = 1, 
# different sex =-1
# So its current value for this actor is: 
# fi(x) = -2.32*(-2.5) + 1.39*1.5 + 0.16*0.5 + # 0.91*(-1) =7.055
```

##### Problem c)

##### Discuss the goodness of fit of the model with regard to the indegree distribution
```{r intr6}
# Calculate the fit with respect to the indegree distribution

# By specifying "verbose=TRUE" we get information on the screen telling how far       
# calculations have progressed.

# From the graph, the red line is observed. X-axes is the drgree from 1 to 8, while   
# the y-axes is the simulated indegree.

# It is a great fit model, the distribution is smooth.However this perfect fitting
# model facing the risk of overfitting. 
```


